Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2021-01-04 revisionMemo2/revisionLetter.tex
start on rr2

% \doublespacing
\def\input@path{
	{C:/Users/Owner/Research/netsMatter/paper/graphics/},
	{C:/Users/herme/Research/netsMatter/paper/graphics/},
	{/Users/s7m/Research/netsMatter/paper/graphics/}
}

\graphicspath{
	{C:/Users/Owner/Research/netsMatter/paper/graphics/},
	{C:/Users/herme/Research/netsMatter/paper/graphics/},
	{/Users/s7m/Research/netsMatter/paper/graphics/},
}

>>>>

% \doublespacing
\def\input@path{
	{C:/Users/Owner/Research/netsMatter/paper/graphics/},
	{C:/Users/herme/Research/netsMatter/paper/graphics/},
	{/Users/s7m/Research/netsMatter/paper/graphics/},
	{/Users/dorffc/ProjectsGit/netsMatter/paper/graphics}
}

\graphicspath{
	{C:/Users/Owner/Research/netsMatter/paper/graphics/},
	{C:/Users/herme/Research/netsMatter/paper/graphics/},
	{/Users/s7m/Research/netsMatter/paper/graphics/},å
	{/Users/dorffc/ProjectsGit/netsMatter/paper/graphics}
}
